Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-06-15 doc/ms.tex
Include updated early light curve figure and new values for the power-law fits in the paper.

As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-lax index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
\begin{equation}
  \label{eq:broken_power_law}
  f(t) \left\{
    \begin{array}{ll}
      = 0,\ \textrm{when}\ t<t_0 \\
      \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
    \end{array}
  \right.\ ,
\end{equation}
where $t_0$ is the time of first light and $\alpha$ is the power-law index. To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc, which were taken exclusively with P48 in the $g_\mathrm{PTF}$ filter. To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
and the proportionality constant, and minimize $\chi^2$. 
The modeling results show that the SN flux rises approximately
linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
the joint marginal distribution of $t_0$ and $\alpha$. With the
best-fit model of $\alpha=0.96$ and $t_0=-18.4$ days, our first
detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
the SN first light.

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.95\textwidth]{early_lc.pdf}
  \caption{Broken Power low fitting to the early $g$-band light
    curve. The best-fit model of $\alpha=0.92$ and $t_0=-18.47\,\textrm{days}$
    and corresponding residues are shown in the top and bottom panels, respectively.
    The joint distribution of $t_0$ and $\alpha$ is illustrated in the inset of
    the upper panel. The solid and dashed contours represent the $68\%$ and $99.7\%$
    confidence levels.
  }
  \label{fig:early_lc_fit}
\end{figure*}

Starting around $t=-15\,\textrm{d}$, the $g$-band light curve 
deviates from the above best-fit model and 
rises significantly faster, indicating a
change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
before $t=-8$\,days can be approximated by a broken power-law model
(e.g.,
\citealt{2016arXiv161202097Z,
  2016arXiv161202725Z}).

@@

% \amiller{Revisit this paragraph in context of discussion -- might need to be moved to later section} As discussed in Section \ref{sec:lc_energy}, the initial light curve
% of \abc\ is probably purely powered by the radioactive decay of
% $^{56}$Ni. Thus, the initial rise of the light curve depends on
% the depth of the shallowest layer where $^{56}$Ni is deposited
% \citep{2014ApJ...784...85P}. According to theoretical models
% \citep{2016ApJ...826...96P}, the linearly rising light curve implies
% strong mixing of $^{56}$Ni in the ejecta. As a result, the time lag
% between the time of explosion and SN first light is negligible.

>>>>

As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-lax index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
\begin{equation}
  \label{eq:broken_power_law}
  f(t) \left\{
    \begin{array}{ll}
      = 0,\ \textrm{when}\ t<t_0 \\
      \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
    \end{array}
  \right.\ ,
\end{equation}
where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the rest-frame of the SN. To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc. Due to slight variations in the passbands, we fit the model to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.

To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
and the proportionality constant, and minimize $\chi^2$. 
The modeling results show that the SN flux rises approximately
linearly between
$t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
the joint marginal distribution of $t_0$ and $\alpha$. With the
best-fit model of $\alpha=0.98$ and $t_0=-17.94$ d, our first
detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
the SN first light. Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point. This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band. Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneous we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above. In the analysis that follows, the precise values of the best-fit parameters is not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.95\textwidth]{early_lc.pdf}
  \caption{Best-fit power-law model to describe the early flux from 
  \abc\ in the $g_\mathrm{PTF}$-band. The model flux, adopting 
  best-fit parameters $\alpha=0.98$ and $t_0=-17.94\,\textrm{d}$, 
  is shown as a solid black line in the top panel. The lower panel 
  shows the model residuals, and the symbols are the same as in
  Figure~\ref{fig:lightcurve}. The model is fit to just the 
  $g_\mathrm{PTF}$-band observations to avoid systematic difference 
  between the filters (see the text for further 
  details). The joint distribution of $t_0$ and $\alpha$ is 
  illustrated in the inset of the upper panel. The solid and 
  dashed contours represent the $68\%$ and $99.7\%$ confidence 
  levels.
  }
  \label{fig:early_lc_fit}
\end{figure*}

% Starting around $t=-15\,\textrm{d}$, the $g$-band light curve
% deviates from the above best-fit model and
% rises significantly faster, indicating a
% change in the power-law index $\alpha$. In fact, between $t=-14\,\mathrm{d}$ and $t=-8\,\mathrm{d}$ the light curve is well fit by a power law of index $1.40$. In other words, the entire light curve
% before $t=-8$\,days can be approximated by a broken power-law model
% (e.g.,
% \citealt{2016arXiv161202097Z,
%   2016arXiv161202725Z}).

@@
